---
title: "Genome-wide mRNA lifetimes and elongation rates"
author:
  - Gwanggyu Sun:
      email: ggsun@stanford.edu
      institute: [SU]
      correspondence: true
  - Stevan Jeknic:
      email: sjeknic@stanford.edu
      institute: [SU]
      correspondence: true
  - Tom Handley:
      email: thandley@stanford.edu
      institute: [SU]
      correspondence: true
institute:
  - SU: Stanford University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
keywords: |
  transcription; mRNA degradation; elongation
highlights: |
  Quantitative halflives and elongation rates for individual mRNA species.
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```


<!-- The actual document text starts here: -->
```{r load, echo = FALSE, results = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(finalproject)
library(gridExtra)
```
# Introduction

Quantitative data regarding the rates of mRNA degradation and transcript elongation
are sparse. Typically, mathematical models involving these processes, use a single
rate constant that applies to all mRNA species. However, recent work[@Chen2015] 
has shown that this assumption is not valid. As such, we focused on using some of
these recently collected data to visualize the distribution of individual mRNA
lifetimes and elongation rates.

# Methods

We are using RNA-seq data that were collected in exponentially growing *E*. *coli*
cells by Chen et al.[@Chen2015].

# Results

<!-- Here's some example analysis code: -->
```{r demo-plot, fig.cap="Plot of mRNA lifetimes (left) and elongation rates (right)", results=FALSE, echo=TRUE}
data_3a <- load_raw_data("supp_table4.csv")
data_3b <- load_raw_data("supp_table6.csv")

plot_3a <- plot_histogram(data_3a, "Avg.lifetime", binwidth=0.5, xh=10, yh=160)
plot_3b <- plot_histogram(data_3b, "Elongation.Rate..nt.s.", binwidth=5, xh=75, yh=70)
grid.arrange(plot_3a, plot_3b, ncol=2)
```

# Acknowledgements

Elliott Hazen, Max Czapanskiy, Maurice Goodman, and Cheyenne Payne for an awesome class!

<!-- The following line inserts a page break  -->

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
